Case for Support

### 2021-11-11 caseForSupport.tex
caseForSupport.tex in progress

@@

A central goal of the software resource proposed here is to address this
problem, by providing Bonsai~(an experimental control software ecosystem;
Figure~\ref{fig:bonsai} and Section~\ref{sec:bonsai}) with state-of-the-art
online (and offline) data analysis methods
(Figure~\ref{fig:proposedBonsaiExtensions} and
Section~\ref{sec:toBeAddedMachineIntelligenceFunctionality}). Bonsai is
\textbf{unique} among experimental control software in that it allows people
with no programming experience to control sophisticated experiments. Its large
and rapidly growing user base demonstrates the need of this type of software
resources. With the proposed functionality to be added to Bonsai, its users
will be able to use sophisticated machine-learning methods to control their
experiments and analyze their data. This popularization of machine learning
functionality will allow scientists without computational skills to control
sophisticated experiments and analyze their data in unprecedented ways, which
will most probably yield important \textbf{advances in science}.

@@

Using the proposed capabilities to communicate Bonsai with software written in
other languages, we will integrate into Bonsai an initial set of state-of-the
art behavioral and neural data analysis methods
(Section~\ref{sec:toBeAddedMachineIntelligenceFunctionality}).

@@

\subsection{Software infrastructure to incorporate machine intelligence
functionality to Bonsai}
\label{sec:softwareInfrastructure}

@@

A central aim of this proposal is to create software infrastructure to provide
this machine intelligence functionality to Bonsai in extensible and general
ways.

\subsubsection{Generality}

@@

\subsubsection{Extensibility}

@@

\subsection{Machine intelligence functionality to be added to Bonsai}
\label{sec:toBeAddedMachineIntelligenceFunctionality}

@@

\subsubsection{Spike sorting}
\label{sec:spikeSorting}

@@

\subsubsection{Low-dimensional representations of spiking data}
\label{sec:lowDimensionalRepresentationsOfSpikingData}

@@

\subsubsection{Low-dimensional representations of local-field potentials}
\label{sec:lowDimensionalRepresentationsOfLFPs}

@@

\subsubsection{Neural decoding}
\label{sec:neuralDecoding}

@@

\subsubsection{Comparing multiple data-analysis methods}
\label{sec:comparisonOfMultipleMethods}

@@

We will demonstrate each machine intelligence functionality added to Bonsai
(Section~\ref{sec:toBeAddedMachineIntelligenceFunctionality}) and the multiple
data-analysis methods comparisons
(Section~\ref{sec:comparisonOfMultipleMethods}) in Bonsai experiments. We will
then distribute Bonsai configuration files for users to reproduce these
demonstrations.

@@

\section{Community demand}

\section{User engagement}

>>>>

\makeatletter
\renewcommand\paragraph{\@startsection{paragraph}{4}{\z@}%
            {-2.5ex\@plus -1ex \@minus -.25ex}%
            {1.25ex \@plus .25ex}%
            {\normalfont\normalsize\bfseries}}
\makeatother
\setcounter{secnumdepth}{4} % how many sectioning levels to assign numbers to
\setcounter{tocdepth}{4}    % how many sectioning levels to show in ToC

@@

A central goal of the software resource proposed here is to address this
problem, by providing Bonsai~(an experimental control software ecosystem;
Figure~\ref{fig:bonsai} and Section~\ref{sec:bonsai}) with state-of-the-art
online (and offline) data analysis methods
(Figure~\ref{fig:proposedBonsaiExtensions} and
Section~\ref{sec:functionality}). Bonsai is
\textbf{unique} among experimental control software in that it allows people
with no programming experience to control sophisticated experiments. Its large
and rapidly growing user base demonstrates the need of this type of software
resources. With the proposed functionality to be added to Bonsai, its users
will be able to use sophisticated machine-learning methods to control their
experiments and analyze their data. This
\textbf{democratisation} of machine learning
functionality will allow scientists without computational skills to control
sophisticated experiments and analyze their data in unprecedented ways, which
will most probably yield important \textbf{advances in science}.

@@

Using the proposed capabilities to communicate Bonsai with software written in
other languages, we will integrate into Bonsai an initial set of state-of-the
art behavioral and neural data analysis methods
(Section~\ref{sec:functionality}).

@@

We intend to improve an \textbf{existing resource}, the Bonsai ecosystem. We
propose to create software infrastructure to facilitate the integration into it
of existing advanced data analysis methods
(Section~\ref{sec:softwareInfrastructure}).
%
To demonstate the use of this infrastructure, and to provide Bonsai users with
an initial set of advanced machine intelligence neural data analysis methods,
we will add to the Bonsai ecosystem machine learning functionality to control
neuroscience experiments and to analyze data generated by them
(Section~\ref{sec:functionality}).

This initial set of methods should demonstrate to Bonsai users, and to
machine-learning methods developers, the potential of embedding
machine-learning functionality into the experimental control loop. We propose
user engagement activities to expose both of these groups of people to this
potential (Section~\ref{sec:userEngagement}).  When data-analysis method
developers recognize this potentials, they will become interested in
contributing their methods to the Bonsai ecosystem, ensuring the
\textbf{long-term sustainability} of the proposed resource.

\subsection{Software infrastructure}
\label{sec:softwareInfrastructure}

@@

We propose to create software infrastructure to add machine intelligence
functionality to the Bonsai ecosystem in general
(Section~\ref{sec:generality}) and extensible ways
(Section~\ref{sec:extensibility}).

\subsubsection{Generality}
\label{sec:generality}

@@

\subsubsection{Extensibility}
\label{sec:extensibility}

@@

\subsection{Machine intelligence functionality to be added to Bonsai}
\label{sec:functionality}

We propose to initially add to Bonsai machine intelligence functionality to
support neuroscience experiments because, currently, neuroscience is the
research area with the largest number of Bonsai users. Within neuroscience, we
propose to add functionality for video-based behavioral analysis
(Section~\ref{sec:videoBasedBehavioralAnalysis}) and for running
brain-computer-interface experiments (Section~\ref{sec:bci}), since these tasks
are relevant to many Bonsai users, and recent advances in machine learning
will greatly improve their implementation in Bonsai.

@@

\subsubsection{Brain-computer-interface applications}
\label{sec:bci}

\paragraph{Spike sorting}
% \label{sec:spikeSorting}

@@

\paragraph{Low-dimensional representations of spiking data}
% \label{sec:lowDimensionalRepresentationsOfSpikingData}

@@

\paragraph{Low-dimensional representations of local-field potentials}
% \label{sec:lowDimensionalRepresentationsOfLFPs}

@@

\paragraph{Neural decoding}
% \label{sec:neuralDecoding}

@@

\paragraph{Comparing multiple data-analysis methods}
% \label{sec:comparisonOfMultipleMethods}

@@

We will demonstrate each machine intelligence functionality added to Bonsai
(Section~\ref{sec:functionality}) and the multiple
data-analysis methods comparisons
(Section~\ref{sec:comparisonOfMultipleMethods}) in Bonsai experiments. We will
then distribute Bonsai configuration files for users to reproduce these
demonstrations.

\subsection{Measurable targets}
\label{sec:measurableTargets}

To assess the progress of the proposed project, we propose the following
measurable targets:

    \item[implementation of software infrastructure]
        (Section~\ref{sec:softwareInfrastructure}) includes the
        implementation of the machine abstractions described in Section~\ref{}
        and of the capabilities to be added to Bonsai to communicate with
        software written in other languages described in Section~\ref{}. We
        will consider this target completed when we can implement a simple BCI
        application, with the architecture depicted in Figure~\ref{}, with
        machine learning functionality provided by software in Python, Matlab
        and R.

    \item[implementation of functionality] (Sections~\ref{sec:functionality})
        includes the integration into Bonsai of machine learning software
        for video-based behavioral analysis (Section~\ref{}) and for
        brain-computer-interface applications (Section~\ref{}). Completion of
        this target requires that Bonsai can perform these tasks interacting
        with software written in other languages.

    \item[internal testing] multiple groups at the SWC use Bonsai to control
        their experiments.

        Bonsai Github repository and the success use by Bonsai users

    \item Bonsai users use the implemented machine learning functionality. We
        propose to evaluate this target by checking in the Bonsai user forum
        the frequency with which a novel machine learning functionality is
        discussed, and by tracking publications using this functionality.

    \item method developers integrate their methods into the Bonsai ecosystem.
        The integration of machine learning functionality into Bonsai will use
        Bonsai's package manager. We propose to use this package manaer to tack
        the number of machine intelligence methods integrated into Bonsai.

@@

\section{Community demand}
\label{sec:communityDemand}

\section{User engagement}
\label{sec:userEngagement}
